---
title: "Plotly Presentation"
author: "Hugo van den Berg"
date: "`r gsub(' +', ' ', format(Sys.Date(), '%B %e, %Y'))`"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyr)
library(dplyr)
library(ggplot2)
library(plotly)
```

## Plotly Presentation

- Comparing lengths and widths of part of iris-flowers
- Do petal length and width show a similar relation as sepal length and width?

## Preparing data

- Dataset `iris` from `datasets` package.
- Separate parts of the flowers into separate observations for facetting in
    `ggplot`.


```{r prep_iris}
iris.semilong <- iris %>%
    tbl_df %>%
    mutate(
        row = rep(1:50, 3) # Row counter necessary for spreading later
        ) %>%
    gather(
        key = Part,
        value = Size,
        -Species,
        -row
        ) %>%
    separate(
        col = Part,
        into = c("Part", "Measure"),
        sep = '\\.'
        ) %>%
    spread(
        key = Measure,
        value = Size
        )
```

## Do the distributions look alike?

```{r plot_iris, echo=FALSE}
g <- iris.semilong %>%
    ggplot(
        aes(
            x = Width,
            y = Length,
            colour = Species
            )
        ) +
    geom_point(
        alpha = .5
        ) +
    stat_ellipse( # 95% confidence ellipse under t-distribution
        alpha = .4
        ) +
    facet_wrap(
        ~Part
        )

ggplotly(g)
```

## Conclusion

- The relation between petal length and petal width is roughly linear, even
    across different species.
- The relation between sepal width and length within each species is roughly
    linear. Across different species there is a much less strong corelation
    between length and width. Notably the setosa flowers have shorter sepals
    for a certain sepal width than the other two species.
